{\bfseries 'D.\-I.\-T}.' A\-P\-I is carefully selected and tightly managed A\-P\-Is from the Tizen native systems. The {\bfseries 'D.\-I.\-T}.' A\-P\-I Specification available in the Tizen Native S\-D\-K shows full list of the selected native subsystem A\-P\-Is. \par
The {\bfseries 'D.\-I.\-T}.' A\-P\-I is divided into dozens of A\-P\-I modules; each module represents a logically similar set of submodule A\-P\-Is, which can be grouped into the same category.\par
\section{Required Header}\label{index_intro}
To be able to use an A\-P\-I, you need to include a header in which A\-P\-I is defined. You can find required headers in A\-P\-I reference as illustrated below\-: \par
 \par
 \section{Feature}\label{index_feature}
Some of the {\bfseries 'D.\-I.\-T}.' A\-P\-Is require features to prevent your application from being shown in the application list on the Tizen store. \par
If related Feature is included in A\-P\-I reference as shown below and your application uses that feature, then you need to declare the feature in the tizen-\/manifest.\-xml file. \par
 \par
 \section{Privilege}\label{index_privilege}
The privilege is essential part to get access grant for privacy related data or sensitive system resources. \par
Some of the {\bfseries 'D.\-I.\-T}.' A\-P\-I A\-P\-I functions require adding appropriate privileges to the tizen-\/manifest.\-xml file. \par
If required privileges are not included in the tizen-\/manifest.\-xml file, then the function will return {\itshape P\-E\-R\-M\-I\-S\-S\-I\-O\-N\-\_\-\-D\-E\-N\-I\-E\-D} error. \par
For example, see the \char`\"{}\-Privilege\-:\char`\"{} section in the following picture\-: \par
 \par
 \section{Structure of Function Descriptions}\label{index_structure}
In the function documentation for each module, the functions are described using a unified structure, illustrated in the below example. \par
 \par
